---
title: "Code to Produce the Venn-Diagrams and Table 2"
author: "Abebe F"
date: "2024-06-07"
output:
  pdf_document: default
  html_document: default
---

```{r}

library(VennDiagram)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)

```

Read the file
```{r}
final <-read.csv('final2.csv', stringsAsFactors = FALSE)
```


Produce the Venn Diagram for the more specific DIVA skin, DIVA IGRA and CCT skin concordant and discordant test outcomes on PM Status
Figure 5 a) and b)

```{r}
control_specific =list(DIVA.Ig = which(unlist(final %>% filter(Treatment=='Control') %>% select(DST1))),
                       DIVA.Sk=which(unlist(final %>% filter(Treatment=='Control') %>% select(DST10))),
                       CCT=which(unlist(final %>% filter(Treatment=='Control') %>% select(CCT))),
                       PM=which(unlist(final %>% filter(Treatment=='Control') %>% select(PM))))

vaccinate_specific =list(DIVA.Ig = which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(DST1))),
                        DIVA.Sk=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(DST10))),
                         CCT=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(CCT))),
                         PM=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PM))))

venn.plot <- venn.diagram(
  control_specific, 
  filename = 'Specific_control.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);


venn.plot <- venn.diagram(
  vaccinate_specific, 
  filename = 'Specific_vaccinate.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);

```

Produce the Venn Diagram for the more sensitive SIT skin, PPD (B-A) IGRA and PPD-B IGRA concordant and discordant test outcomes on PM status
Figure 5 C) and d)

```{r}
control_sensitive =list(SIT = which(unlist(final %>% filter(Treatment=='Control') %>% select(SIT))),
                        'PPD(B-A)'=which(unlist(final %>% filter(Treatment=='Control') %>% select(PPD_BA))),
                        'PPD-B'=which(unlist(final %>% filter(Treatment=='Control') %>% select(PPD_B))),
                        PM=which(unlist(final %>% filter(Treatment=='Control') %>% select(PM))))

vaccinate_sensitive =list(SIT = which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(SIT))),
                          'PPD(B-A)'=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PPD_BA))),
                          'PPD-B'=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PPD_B))),
                          PM=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PM))))

venn.plot <- venn.diagram(
  control_sensitive, 
  filename = 'Sensitive_control.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);


venn.plot <- venn.diagram(
  vaccinate_sensitive, 
  filename = 'Sensitive_vaccinate.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);

```


Skin Test Response on PM Status Grouped by Treatments 
Supplementary Figure S3 a) and b)

```{r}
control_skin_test =list(SIT = which(unlist(final %>% filter(Treatment=='Control') %>% select(SIT))), 
                       DIVA.Sk=which(unlist(final %>% filter(Treatment=='Control') %>% select(DST10))),
                       CCT=which(unlist(final %>% filter(Treatment=='Control') %>% select(CCT))),
                       PM=which(unlist(final %>% filter(Treatment=='Control') %>% select(PM))))

vaccinate_skin_test =list(SIT = which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(SIT))), 
                         DIVA.Sk=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(DST10))),
                         CCT=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(CCT))),
                         PM=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PM))))

venn.plot <- venn.diagram(
  control_skin_test, 
  filename = 'skin_test_control.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);


venn.plot <- venn.diagram(
  vaccinate_skin_test, 
  filename = 'skin_test_vaccinate.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);
```


IGRA Test Response on PM Status Grouped by Treatments 
Supplementary Figure S3 c) and d)

```{r}
control_IGRA_Test =list(DIVA.Ig = which(unlist(final %>% filter(Treatment=='Control') %>% select(DST1))),
                        'PPD(B-A)'=which(unlist(final %>% filter(Treatment=='Control') %>% select(PPD_BA))),
                        'PPD-B'=which(unlist(final %>% filter(Treatment=='Control') %>% select(PPD_B))),
                        PM=which(unlist(final %>% filter(Treatment=='Control') %>% select(PM))))

vaccinate_IGRA_Test =list(DIVA.Ig = which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(DST1))),
                          'PPD(B-A)'=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PPD_BA))),
                          'PPD-B'=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PPD_B))),
                          PM=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PM))))

venn.plot <- venn.diagram(
  control_IGRA_Test, 
  filename = 'IGRA_Test_control.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);


venn.plot <- venn.diagram(
  vaccinate_IGRA_Test, 
  filename = 'IGRA_Test_vaccinate.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);
```

Skin Test Response on M_bovis PCR Status Grouped by Treatments 
Supplementary Figure S4 a) and b)

```{r}
control_skin_test_Vs_PCR =list(SIT = which(unlist(final %>% filter(Treatment=='Control') %>% select(SIT))), 
                        DIVA.Sk=which(unlist(final %>% filter(Treatment=='Control') %>% select(DST10))),
                        CCT=which(unlist(final %>% filter(Treatment=='Control') %>% select(CCT))),
                        PCR=which(unlist(final %>% filter(Treatment=='Control') %>% select(PCR))))

vaccinate_skin_test_Vs_PCR =list(SIT = which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(SIT))), 
                          DIVA.Sk=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(DST10))),
                          CCT=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(CCT))),
                          PCR=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PCR))))

venn.plot <- venn.diagram(
  control_skin_test_Vs_PCR, 
  filename = 'skin_test_control_on_PCR.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);


venn.plot <- venn.diagram(
  vaccinate_skin_test_Vs_PCR, 
  filename = 'skin_test_vaccinate_on_PCR.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);

```


IGRA Test Response on PM Status Grouped by Treatments 
Supplementary Figure S4 c) and d)

```{r}
control_IGRA_Test_Vs_PCR =list(DIVA.Ig = which(unlist(final %>% filter(Treatment=='Control') %>% select(DST1))),
                        'PPD(B-A)'=which(unlist(final %>% filter(Treatment=='Control') %>% select(PPD_BA))),
                        'PPD-B'=which(unlist(final %>% filter(Treatment=='Control') %>% select(PPD_B))),
                        PCR=which(unlist(final %>% filter(Treatment=='Control') %>% select(PCR))))

vaccinate_IGRA_Test_Vs_PCR =list(DIVA.Ig = which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(DST1))),
                          'PPD(B-A)'=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PPD_BA))),
                          'PPD-B'=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PPD_B))),
                          PCR=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PCR))))

venn.plot <- venn.diagram(
  control_IGRA_Test_Vs_PCR, 
  filename = 'IGRA_Test_control_on_PCR.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);


venn.plot <- venn.diagram(
  vaccinate_IGRA_Test_Vs_PCR, 
  filename = 'IGRA_Test_vaccinate_on_PCR.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);

```



```{r}
library(sjPlot)
library(gtsummary)
```
```{r}
names(final)
```
Summary of Skin and IGRA Test positives classified by PCR alone, Gross VL alone as well as either of Gross VL, Culture and PCR for Table 2


```{r}
library(gtsummary)
final %>%
select(Treatment, DST10, CCT, SIT, DST1, PPD_BA, PPD_B, PM, Fasciola,PCR, Gross_VL  ) %>%
tbl_summary(by = Treatment) %>%
  add_p() %>% 
  add_overall() 
```

```{r}
final %>%
  select(Treatment, DST10, CCT, SIT, DST1, PPD_BA, PPD_B, PM, Fasciola,PCR, Gross_VL  ) %>%
  tbl_strata(
    strata = PCR, 
    ~.x %>% 
      tbl_summary(by = Treatment)) 
```




```{r}
final %>%
  select(Treatment, DST10, CCT, SIT, DST1, PPD_BA, PPD_B, PM, Fasciola,PCR, Gross_VL  ) %>%
  tbl_strata(
    strata = PM, 
    ~.x %>% 
      tbl_summary(by = Treatment))
```

```{r}
library(gtsummary)
final %>%
  select(Treatment, DST10, CCT, SIT, DST1, PPD_BA, PPD_B, PM, Fasciola,PCR, Gross_VL  ) %>%
  tbl_strata(
    strata = Gross_VL, 
    ~.x %>% 
      tbl_summary(by = Treatment))

```

