---
title: "Code to Produce Fig 4. The Venn-Diagrams"
author: "Abebe F"
date: "2024-06-07"
output: html_document
---

```{r}

library(VennDiagram)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)

```

Read the file
```{r}
final <-read.csv('final2.csv', stringsAsFactors = FALSE)
```


Produce the Venn Diagram for the more specific DIVA skin, DIVA IGRA and CCT skin concordant and discordant test outcomes


```{r}
control_specific =list(DIVA.Ig = which(unlist(final %>% filter(Treatment=='Control') %>% select(DST1))),
                       DIVA.Sk=which(unlist(final %>% filter(Treatment=='Control') %>% select(DST10))),
                       CCT=which(unlist(final %>% filter(Treatment=='Control') %>% select(CCT))),
                       PM=which(unlist(final %>% filter(Treatment=='Control') %>% select(PM))))

vaccinate_specific =list(DIVA.Ig = which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(DST1))),
                        DIVA.Sk=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(DST10))),
                         CCT=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(CCT))),
                         PM=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PM))))

venn.plot <- venn.diagram(
  control_specific, 
  filename = 'Specific_control.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);


venn.plot <- venn.diagram(
  vaccinate_specific, 
  filename = 'Specific_vaccinate.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);

```

Produce the Venn Diagram for the more specific DIVA skin, DIVA IGRA and CCT skin concordant and discordant test outcomes

```{r}
control_sensitive =list(SIT = which(unlist(final %>% filter(Treatment=='Control') %>% select(SIT))),
                        'PPD(B-A)'=which(unlist(final %>% filter(Treatment=='Control') %>% select(PPD_BA))),
                        'PPD-B'=which(unlist(final %>% filter(Treatment=='Control') %>% select(PPD_B))),
                        PM=which(unlist(final %>% filter(Treatment=='Control') %>% select(PM))))

vaccinate_sensitive =list(SIT = which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(SIT))),
                          'PPD(B-A)'=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PPD_BA))),
                          'PPD-B'=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PPD_B))),
                          PM=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PM))))

venn.plot <- venn.diagram(
  control_sensitive, 
  filename = 'Sensitive_control.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);


venn.plot <- venn.diagram(
  vaccinate_sensitive, 
  filename = 'Sensitive_vaccinate.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);

```
##################################################################
# Venn Diagram by skin and IGRA tests for both control and vaccinated groups 

#########################

control_skin_test =list(SIT = which(unlist(final %>% filter(Treatment=='Control') %>% select(SIT))), 
                       DIVA.Sk=which(unlist(final %>% filter(Treatment=='Control') %>% select(DST10))),
                       CCT=which(unlist(final %>% filter(Treatment=='Control') %>% select(CCT))),
                       PM=which(unlist(final %>% filter(Treatment=='Control') %>% select(PM))))

vaccinate_skin_test =list(SIT = which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(SIT))), 
                         DIVA.Sk=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(DST10))),
                         CCT=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(CCT))),
                         PM=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PM))))

venn.plot <- venn.diagram(
  control_skin_test, 
  filename = 'skin_test_control.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);


venn.plot <- venn.diagram(
  vaccinate_skin_test, 
  filename = 'skin_test_vaccinate.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);
##########################

control_IGRA_Test =list(DIVA.Ig = which(unlist(final %>% filter(Treatment=='Control') %>% select(DST1))),
                        'PPD(B-A)'=which(unlist(final %>% filter(Treatment=='Control') %>% select(PPD_BA))),
                        'PPD-B'=which(unlist(final %>% filter(Treatment=='Control') %>% select(PPD_B))),
                        PM=which(unlist(final %>% filter(Treatment=='Control') %>% select(PM))))

vaccinate_IGRA_Test =list(DIVA.Ig = which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(DST1))),
                          'PPD(B-A)'=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PPD_BA))),
                          'PPD-B'=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PPD_B))),
                          PM=which(unlist(final %>% filter(Treatment=='Vaccinate') %>% select(PM))))

venn.plot <- venn.diagram(
  control_IGRA_Test, 
  filename = 'IGRA_Test_control.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);


venn.plot <- venn.diagram(
  vaccinate_IGRA_Test, 
  filename = 'IGRA_Test_vaccinate.tiff',
  col = "transparent",
  fill = c("lightblue", "lightgreen", "lightcoral", "plum"),
  alpha = 0.50,
  label.col = c("black"),
  cex = 1.5,
  fontfamily = "serif",
  fontface = "bold",
  cat.col = c("blue", "darkgreen", "red", "purple"),
  cat.cex = 1.5,
  cat.pos = c(-10, 15, -15, 0), # Move labels upwards considerably\
  cat.dist = c(0.22, 0.22, 0.12, 0.12), # Adjust distances\
  cat.fontfamily = "sans",
  rotation.degree = 0, 
  margin = 0.2);

##############################

